```{r}
devtools::load_all()
library(MarrMot)
library(Ipaper)
library(dplyr)
library(hydroTools)
library(sf)
library(data.table)
library(magrittr)

split_site <- function(x, site = "name") {
  split(select(x, -all_of(site)), x[[site]])
}
```

```{r}
indir <- "Z:/DATA/China/ChinaRunoff_latest/ChinaBasins"

shp <- read_sf(glue("{indir}/ChinaBasins_(塔河+雅江+长江+黄河+珠江)-sp375_v0.1.0.shp"))
lst <- readRDS(glue("{indir}/ChinaBasins_气象驱动-sp375.RDS")) # meteorological forcing
load(glue("{indir}/ChinaBasins_(塔河+雅江+长江+黄河+珠江)-sp375_v0.1.0.rda")) # runoff data

get_input <- function(site) {
  shp_i <- shp %>% subset(name == site)
  lat <- st_coordinates(shp_i) %>%
    {
      mean(.[, 2])
    }
  area <- shp_i$area_w_km2 * 1e4 # km^2

  forcing <- lst[[site]][year(date) >= 2012] %>%
    set_names(c("date", "Rl", "prcp", "Pa", "q", "Rsi", "Tavg", "Tmax", "Tmin", "U10"))
  forcing <- forcing %>%
    mutate(
      prcp = round(prcp * 24, 2), # mm hr-1, mm/d
      Pa = Pa / 1e3, # Pa, kPa
      Tavg = K2T(Tavg),
      Tmax = K2T(Tmax),
      Tmin = K2T(Tmin),
      # RH = q2RH(q, Tavg, Pa), # kg/kg, kPa
      ea = q2ea(q, Pa),
      # D2 = cal_es(Tavg) - ea,
      D = (cal_es(Tmin) + cal_es(Tmax)) / 2 - ea,
      Rn = cal_Rn(lat, date, Rsi, Tmin, Tmax, ea = ea)$Rn,
      ET0 = ET0_FAO98(Rn, Tavg, Pa, D, U10, z.wind = 10)$ET0
    )
  data <- df_river[name == site][year(date) >= 2002, -(1:2)] %>%
    dplyr::rename(Qobs = Q) %>%
    merge(forcing[, .(date, prcp, ET0)])
  list(data = data, area = area, lat = lat, site = site)
}

# srad: `W m-2`
# lrad: `W m-2`
# MJ m-2 d-1
```

```{r}
```{r}
# 水库："万家寨上"
sites = c(
  "巴彦高勒", "三湖河口", "包头", "头道拐", "府谷"
) # , "温家川"

l_Q  = df_river[name %in% sites] %>% split_site() %>% .[sites]
l_met = lst_mete[sites]
shps = shps_all %>% subset(name %in% sites) %>% 
  mutate(name = factor(name, sites)) %>% arrange(name)


l_forcing = foreach(d_Q = l_Q, d_met = l_met, i = icount()) %do% {
  shp = shps[i,]
  area = shp$area_w_km2
  
  d = merge(d_Q, d_met) %>% 
    mutate(area_w = area, R = Q2R(Q, area*1e4), .before = "Q")
}

info[name %in% sites]
```

```{r}

# 统计每个站点的数据开始时间和缺测时间，以及数据缺失情况
get_baseInfo <- function(d) {
  date_begin = min(d$date)
  date_end = max(d$date)
  
  dates_full = seq(date_begin, date_end, by = "day")
  n_all = length(dates_full)
  n_valid = sum(!is.na(d$Q))
  n_miss = n_all - n_valid
  perc_miss = n_miss / n_all * 100

  sname = c("min", "1st.Qu.", "median", "3rd.Qu", "max")
  d2 = quantile(d$Q, c(0, 0.25, 0.5, 0.75, 1), na.rm = TRUE) %>% 
    set_names(paste0("Q_", sname)) %>% as.list() %>% as.data.table()
  # d2 = summary(d$Q) %>% 
  data.table(date_begin, date_end, n_all, n_valid, n_miss, perc_miss) %>% 
    cbind(d2)
}

info_Q = map(l_Q, get_baseInfo) %>% melt_list("site") %>% 
  mutate(site = factor(site, sites)) %>% 
  arrange(site)
info_Q 
```

```{r}
info_Q %>% select(site, Q_min:Q_max)
```

> 结论：
- 温家川：属于小流域
- 包头：流域面积提取错误

```{r}
save(l_Q, l_met, shps, l_forcing, info_Q, file = "data-raw/鄂尔多斯_水文数据.rda")
```
